Analysis for Biracial Grade Retention Project

### 2021-11-24 analysis/analysis.Rmd
Change title of analylsis.Rmd
Insert missing quotation mark

---
title: "Analysis for Project"
output: 
  rmdformats::robobook:
    highlight: tango
    toc_depth: 2
    fig_height: 6
    fig_width: 9
---

@@

```{r cond-means-model-compare, fig.height=12, warning=FALSE, caption="Probability of being behind grade for biracial respondents in comparison to their monoracial comparison groups. 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level. Each panel is based on a different model that accounts for certain variables. Subsequent panels cumulatively include all prior terms.}
#calculate remaining marginal means
coef_table_mod1 <- calculate_marg_means(model1)
coef_table_mod2 <- calculate_marg_means(model2)

>>>>

---
title: "Analysis for Biracial Grade Retention Project"
output: 
  rmdformats::robobook:
    highlight: tango
    toc_depth: 2
    fig_height: 6
    fig_width: 9
---

@@

```{r cond-means-model-compare, fig.height=12, warning=FALSE, caption="Probability of being behind grade for biracial respondents in comparison to their monoracial comparison groups. 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level. Each panel is based on a different model that accounts for certain variables. Subsequent panels cumulatively include all prior terms."}
#calculate remaining marginal means
coef_table_mod1 <- calculate_marg_means(model1)
coef_table_mod2 <- calculate_marg_means(model2)
